### 2008-12-20 talk/ecoop2009/rainbow.tex
put two code snippets side by side, and fix a typo

\begin{figure}[h]
\begin{center}
\input{tlc-folded-virtualized.py}
\caption{The result of virtualizing the \lstinline{stack} list}
\label{fig:tlc-main}
\end{center}
\end{figure}

@@

Promotion is invoked with the use of a hint as well:
\texttt{v2 = hint(v1, promote=True)}.
This hint is a \emph{local} request for \texttt{v2} to be green, without
requiring \texttt{v1} to be green.  Note that this amounts to copying
a red value into a green one, which is not possible in classical
approaches to partial evaluation. A slightly different hint can be used to
promote the \emph{class} of an instance. This is done with
\lstinline{hint(v1, promote_class=True)}. It does not have an effect on the
bindings of any variable.

@@

\begin{figure}[h]
\begin{center}
\begin{lstlisting}[language=Python]
def interp_eval(code, pc, args, pool):
    code_len = len(code)
    stack = []
    while pc < code_len:
        opcode = ord(code[pc])
        opcode = hint(opcode, concrete=True)
        pc += 1

        if opcode == PUSH:
            ...
        elif opcode == LT:
            a, b = stack.pop(), stack.pop()
            hint(a, promote_class=True)
            hint(b, promote_class=True)
            stack.append(IntObj(b.lt(a)))
\end{lstlisting}
\caption{Usage of hints in TLC's main loop}
\label{fig:tlc-main-hints}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\begin{lstlisting}[language=Python]
class IntObj(Obj):
    ...
    def lt(self, other): 
        return self.value < other.int_o()
    def sub(self, other):
        return IntObj(self.value - other.int_o())
    def int_o(self):
        return self.value
\end{lstlisting}
\caption{Excerpt of the \lstinline{IntObj} class}
\label{fig:tlc-intobj}
\end{center}
\end{figure}

>>>>

\begin{figure}[h]
\begin{center}
\input{tlc-folded-virtualized.py}
\caption{The result of virtualizing the \lstinline{stack} list}
\label{fig:tlc-folded-virtualized}
\end{center}
\end{figure}

@@

Promotion is invoked with the use of a hint as well:
\lstinline{v2 = hint(v1, promote=True)}.
This hint is a \emph{local} request for \texttt{v2} to be green, without
requiring \texttt{v1} to be green.  Note that this amounts to copying
a red value into a green one, which is not possible in classical
approaches to partial evaluation. A slightly different hint can be used to
promote the \emph{class} of an instance. This is done with
\lstinline{hint(v1, promote_class=True)}. It does not have an effect on the
bindings of any variable.

@@

\begin{figure}[h]
\begin{center}
\begin{tabular}{l|l}
\begin{lstlisting}
def interp_eval(code, pc, args, pool):
  code_len = len(code)
  stack = []
  while pc < code_len:
      opcode = ord(code[pc])
      opcode = hint(opcode, concrete=True)
      pc += 1

      if opcode == PUSH:
          ...
      elif opcode == LT:
        a, b = stack.pop(), stack.pop()
        hint(a, promote_class=True)
        hint(b, promote_class=True)
        stack.append(IntObj(b.lt(a)))
\end{lstlisting}
&
\hspace{2pt}
\begin{lstlisting}
class IntObj(Obj):

  def lt(self, other): 
    return (self.value < 
            other.int_o())

  def sub(self, other):
    return IntObj(self.value -
                  other.int_o())

  def int_o(self):
    return self.value

  ...
\end{lstlisting}
\end{tabular}
\end{center}
\caption{Usage of hints in TLC's main loop and excerpt of the \lstinline{IntObj} class}
\label{fig:tlc-main-hints}
\end{figure}
